---
title: "Data Pre-Processing"
output:
  html_document: default
  html_notebook: default
---
## Introduction

This exploration of data wrangling is based on [`Applied Predictive Modeling`]("http://amzn.to/2qUOSuO"), chapter 3, "Data Pre-Processing"

## Setup

The data represent information about movies combined from two sources, Rotten Tomatoes and IMDB (Internet Movie Database).

Data: [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged).

Load the dataset into memory:
```{r results='hide'}
load('movies_merged')
```

Load the R packages we'll need:
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(caret)
```

## Data

We can see from a list of the columns that the dataset has a lot to do with ratings and reviews
```{r}
df = movies_merged
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

### 1. Remove non-movie rows

```{r}
df <- filter(df, Type == 'movie')
dim(df)
```

### 2. Drop rows with missing `Gross` value

Since our goal is to model `Gross` revenue against other variables, rows that have missing `Gross` values are not useful to us.

```{r}
df <- filter(df, !is.na(Gross))
dim(df)
```

### 3. Initial model

How well can we model the data without pre-processing any of the features? Let's find out:

Split the data into train and test (not using cross validation):

```{r}
set.seed(1)
inTrainingSet <- caret::createDataPartition(df$Gross, p = 0.8, list = FALSE)
trainingSet <- df[inTrainingSet,]
testSet <- df[-inTrainingSet,]
```
Train a model on all available features:
```{r}
fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated n times
                           repeats = 1)

model <- train(Gross ~ ., data = trainingSet, 
                 method = "lm", 
                 trControl = fitControl,
                 na.rm = TRUE)

model
```

Too many missing values. We could try limiting ourselves to complete cases (no NAs) and try again:

```{r}
trainingSet <- trainingSet %>% drop_na()
dim(trainingSet)
```

